\documentclass{book}
\begin{document}
\begin{flushright}
\texttt{INTRODUCTION}
\hspace*{0.5cm}
\textbf{15}
\end{flushright}
\vspace*{0.7cm}
new tools for quality research  as well as the exploration of new fields of knowledge. But
the e-researcher must also have a set of research skills necessary to conduct quality e-research.
Theses skills are twofold: Internet skills (self-efficacy, mental models, access,
terminology, experience, and trouble shooting) and research skills (problem statement,
literature review, data collection, data analysis, and dissemination).
\begin{flushleft}
\end{flushleft}
\texttt{REFERENCES}
\hspace*{0.5cm}
\end{flushleft}
\vspace*{0.3cm}
Anderson, T.,Rouker, L.,Garrison, R., &Archer, W.(2001).Assessing teaching
\\\hspace*{0.5cm}presence in computer conference transcripts.\emph{Journal of Distance Education},
\\\hspace*{0.5cm}15(1),7-23.
\\Bandura, A.(1977). Self-efficancy:Toward a unifying theory of behavioral change.
\\\hspace*{0.5cm}\emph{Psychological Review,}84, 191-215
\\Benedikt, M.(1991). Cyberspace: Some proposals, In M. Benedikt (Ed.),
\\\hspace*{0.5cm}\emph{Cyberspace: First Steps} (pp.119-224).Cambridge, MA:MTT Press.
\\Bradley,J.(2000.January). Online business still needs the basics.
\\\hspace*{0.5cm}\emph{Washington CEO,}[Online]. Available:http://www.washingtonceo.com
\\\hspace*{0.5cm}/arc-hive/jan00/0100-E-Com.html.
\\Clarke,R.(2001).\emph{Information wants to be free}.[Online].Available://www.edu.ua
\\\hspace*{0.5cm}/people/Roger.Clark/II/IWtbF.html.
\\Eastin M., &LaRose, R.(2001).Internet self-efficancy and the psychology of the digital divide.
\\\hspace*{0.5cm}\emph{Journal of Computer Mediated Communications}, 6(1).[Online].Available: http
\\\hspace*{0.5cm}://www.ascusc.org/jcmc/vol6/issue1/eastin.html.
\\Jenkins, S.(2000)\emph{Internet glossary}.[Online].Available:http://www.unisa.edu.au
\\\hspace*{0.5cm}/itsuhelpdesk/faqs/glossary.html.
\\Stefik,M.(1996).Internet dreams:Acbetypes,mytbs,and metapbors.Cambridge,
\\\hspace*{0.5cm}MA:MTT Press.
\\Wing,K.Whitehead,P.&Maran<R.(1999).Internet and World Wide Web Simplified
\\\hspace*{0.5cm}(3rd ed.).New York:Wiley.
\end{document} 